Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping

### 2018-01-30 stp/paper_aaai/main.tex
link to supplementary

We formulate the problem of semantic labeling as a multi-class classification
problem.
The known source descriptions $\Delta_T$ provide us the training sample.
We compute a feature vector for each attribute in a data source and associate 
the known semantic type with the corresponding feature vector.
The feature vector includes, among others, characteristics
such as a number 
of whitespaces and other special characters, statistics of 
values in the column. 
\forijcai{A full list can be found in Appendix \ref{Ann:SemLab}.}
%\npr{If I remove entropy descr, we are perfectly within page limit}
%\ignore{
One of the important features characterising information content of an attribute is Shannon's entropy.
% of the attribute's concatenated rows
Shannon's entropy 
%(or information entropy~\cite{Manning:Introduction})
 of a string $X$ is defined as
$H(X) = -\sum_{i}{p_i \log_{2}p_i},$ where $p_i$ is the probability of a character, whose index in character vocabulary is $i$, to appear in $X$, and the summation ranges over all
characters in the vocabulary.
%of all possible characters
To evaluate $p_i$ in Shannon's entropy, we evaluate normalized character frequency distribution \emph{chardist} of an attribute, as character counts in concatenated rows of the attribute, normalized by the total length of the concatenated rows.
The alphabet\forijcai{vocabulary of all characters} consists of 100 printable characters\forijcai{ (including $\backslash$n)}.
Finally, we add the 100-dimensional vector of $p_i$ to the attribute feature vector.
%}
We also compute a set of features based on similarity metrics inspired by state-of-the-art works by ~\citeasnoun{Pham:semantic} or~\citeasnoun{Ritze:matching}.
Among others, we compute mean cosine similarity for character distributions of attribute values and string similarity metrics for attribute names.
%To extract features from attribute names, we compute string similarity metrics: minimum edit distance, two WordNet based similarity measures such as JCN~\cite{Jiang:Semantic} and LIN ~\cite{Lin:Information}, and $k$-nearest neighbors using Needle-Wunsch distance~\cite{Needleman:General}.
%The minimum edit distance between two strings $s_1$ and $s_2$ is the minimum number of edit operations, such as insertion, deletion, substitution, which are required to transform one string into another~\cite{Manning:Introduction}.
%We compute the similarity between attribute name and all class instances in the training data.
%The number of thus extracted features depends on the number of semantic labels in the training data.
We train a random forest on the obtained sample.

@@

\begin{figure}[ht]
\centering \scalebox{0.8}{
\begin{tikzpicture}[scale=0.9]
\begin{scope}[xshift=-10]

@@

\begin{figure}[ht]
\centering \scalebox{0.8}{
\begin{tikzpicture}[scale=0.9]
\begin{scope}
	\node[class, rectangle, rounded corners] (CLASS) at (0,0) { \small{ 
	Class nodes of Alignment Graph (i.e. $\mathcal{C_{G_O}}$)}};

>>>>

We formulate the problem of semantic labeling as a multi-class classification
problem.
The known source descriptions $\Delta_T$ provide us the training sample.
We compute a feature vector for each attribute in a data source and associate 
the known semantic type with the corresponding feature vector.
The feature vector includes, among others, characteristics
such as a number 
of whitespaces and other special characters, statistics of 
values in the column\footnote{Full list of features: https://git.io/vN92f (anonymously hosted)}. 
\forijcai{A full list can be found in Appendix \ref{Ann:SemLab}.}
%\npr{If I remove entropy descr, we are perfectly within page limit}
%\ignore{
One of the important features characterising information content of an attribute is Shannon's entropy.
% of the attribute's concatenated rows
Shannon's entropy 
%(or information entropy~\cite{Manning:Introduction})
 of a string $X$ is defined as
$H(X) = -\sum_{i}{p_i \log_{2}p_i},$ where $p_i$ is the probability of a character, whose index in character vocabulary is $i$, to appear in $X$, and the summation ranges over all
characters in the vocabulary.
%of all possible characters
To evaluate $p_i$ in Shannon's entropy, we evaluate normalized character frequency distribution \emph{chardist} of an attribute, as character counts in concatenated rows of the attribute, normalized by the total length of the concatenated rows.
The alphabet\forijcai{vocabulary of all characters} consists of 100 printable characters\forijcai{ (including $\backslash$n)}.
Finally, we add the 100-dimensional vector of $p_i$ to the attribute feature vector.
%}
We also compute a set of features based on similarity metrics inspired by state-of-the-art works by ~\citeasnoun{Pham:semantic} or~\citeasnoun{Ritze:matching}.
Among others, we compute mean cosine similarity for character distributions of attribute values and string similarity metrics for attribute names.
%To extract features from attribute names, we compute string similarity metrics: minimum edit distance, two WordNet based similarity measures such as JCN~\cite{Jiang:Semantic} and LIN ~\cite{Lin:Information}, and $k$-nearest neighbors using Needle-Wunsch distance~\cite{Needleman:General}.
%The minimum edit distance between two strings $s_1$ and $s_2$ is the minimum number of edit operations, such as insertion, deletion, substitution, which are required to transform one string into another~\cite{Manning:Introduction}.
%We compute the similarity between attribute name and all class instances in the training data.
%The number of thus extracted features depends on the number of semantic labels in the training data.
We train a random forest on the obtained sample.

@@

\begin{figure}[ht]
	\vspace*{-3mm}
\centering \scalebox{0.8}{
\begin{tikzpicture}[scale=0.9]
\begin{scope}[xshift=-10]

@@

\begin{figure}[ht]
	\vspace*{-3mm}
\centering \scalebox{0.8}{
\begin{tikzpicture}[scale=0.9]
\begin{scope}
	\node[class, rectangle, rounded corners] (CLASS) at (0,0) { \small{ 
	Class nodes of Alignment Graph (i.e. $\mathcal{C_{G_O}}$)}};
